\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-04-11 paper/main.tex
.

\title[\name{}]{\name{}: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction}
\author[Sample \textit{et~al}.]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
$^{\text{\sf 2}}$Department, Institution, City, Post Code,
Country.}

>>>>

\title[\name{}]{\name{}: Combining Bottom-up and top-down approaches
  through graph learning over interaction networks for
  drug-target-interaction prediction} \author[Sample
\textit{et~al}.]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert
  Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
  $^{\text{\sf 2}}$Computational Bioscience Research Center, Computer,
  Electrical and Mathematical Sciences \& Engineering Division, King
  Abdullah University of Science and Technology, 4700 King Abdullah
  University of Science and Technology, Thuwal 23955, Saudi Arabia.}
